This is an example of article title

### 2025-10-31 paper/paper.tex
minor improvements

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}
\usepackage{amsmath,booktabs,mathtools,amssymb}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.18}

@@

The overall ODE has the form
\begin{equation*}
    \frac{d}{dt}\begin{pmatrix} g \\ \dot{g} \end{pmatrix}
    = \begin{pmatrix} \dot{g} \\ f(t, g, \dot{g}) \end{pmatrix},
\end{equation*}
where \(g \in \mathcal G_1\) and \(f(t, g, \dot{g})\) is derived from the above equations. We further require initial conditions for both \(g\) and \(\dot{g}\) at time \(t_0=0\).
Then this can be solved using Lie group methods, such as the Runge-Kutta-Munthe-Kaas (RKMK) variant \cite{Munthe-Kaas:1998} of Heun's method~\cite[App.~A.1]{IserlesMunthe-KaasNoersettZanna:2000}.

Code~\ref{lst:rod-dynamics} shows functions that calculate the right hand side of the ODE, where \lstinline{E_field} is a function that calculates electric field strength from the point charges at the given point.
The function \lstinline{force_and_torque} calculates the force and torque affecting the rod, while \lstinline{dynamics} converts them to the Lie algebra element can be used by the solver.
\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:rod-dynamics},
    caption={Dynamics of a rod affected by point charges.},
    mathescape
]
function force_and_torque(
        sp::SystemParameters, Fθ, r
    )
    u, u${}_\perp$ = eachrow(Fθ)
    F, $\tau$ = zeros(2), 0.0
    for s in range(-sp.L/2, sp.L/2; length=Nq)
        E = E_field(sp, r .+ s .* u)
        F .+= sp.$\lambda$ * E * (sp.L/(Nq-1))
        $\tau$ += sp.$\lambda$ * s * dot(u${}_\perp$, E) * (sp.L/(Nq-1))
    end
    return F, $\tau$
end
# f((p,θ), (dp,dθ), t) including system parameters
function dynamics(state, sp::SystemParameters, t)
    p, dp = state.x
    F, tau = force_and_torque(sp, p.x...)
    a = F ./ sp.M
    coords = [tau / sp.Icm, a...]
    ddx = hat(sp.se2, coords, ArrayPartition)
    return ArrayPartition(dp, ddx)
end
\end{lstlisting}

@@

\input{bib.tex}
\end{document}

>>>>

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}
\usepackage{amsmath,booktabs,mathtools,amssymb}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{balance}
\pgfplotsset{compat=1.18}

@@

The overall ODE has the form
\begin{equation*}
    \frac{d}{dt}\begin{pmatrix} g \\ \dot{g} \end{pmatrix}
    = \begin{pmatrix} \dot{g} \\ f(g, \dot{g}, t) \end{pmatrix},
\end{equation*}
where \(g \in \mathcal G_1\) and \(f(g, \dot{g}, t)\) is derived from the above equations. We further require initial conditions for both \(g\) and \(\dot{g}\) at time \(t_0=0\).
Then this can be solved using Lie group methods, such as the Runge-Kutta-Munthe-Kaas (RKMK) variant \cite{Munthe-Kaas:1998} of Heun's method~\cite[App.~A.1]{IserlesMunthe-KaasNoersettZanna:2000}.

Code~\ref{lst:rod-dynamics} shows functions that calculate the right hand side of the ODE, where \lstinline{E_field} is a function that calculates electric field strength from the point charges at the given point.
The function \lstinline{force_and_torque} calculates the force and torque affecting the rod, while \lstinline{dynamics} converts them to the Lie algebra element can be used by the solver.
\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:rod-dynamics},
    caption={Dynamics of a rod affected by point charges.},
    mathescape
]
function force_and_torque(
        sp::SystemParameters, Fθ, r
    )
    u, u${}_\perp$ = eachrow(Fθ)
    F, $\tau$ = zeros(2), 0.0
    for s in range(-sp.L/2, sp.L/2; length=Nq)
        E = E_field(sp, r .+ s .* u)
        F .+= sp.$\lambda$ * E * (sp.L/(Nq-1))
        $\tau$ += sp.$\lambda$ * s * dot(u${}_\perp$, E) * (sp.L/(Nq-1))
    end
    return F, $\tau$
end
# f((p,θ), (dp,dθ), t) where (p,θ) and (dp,dθ) are
# passed as the first argument, system parameters
# as the second one and time as the last one
function dynamics(state, sp::SystemParameters, t)
    p, dp = state.x
    F, tau = force_and_torque(sp, p.x...)
    a = F ./ sp.M
    c = [tau / sp.Icm, a...]
    ddx = hat(sp.lie_algebra, c, ArrayPartition)
    return ArrayPartition(dp, ddx)
end
\end{lstlisting}

@@

 \balance
\input{bib.tex}
\end{document}
